### 2018-05-16 msc_diploma_cubesat_galgoczi.tex
update

@@

\subsection{The simulated setup}

esr foil:
Please check "ESR from 3M" company. e.g.,
%http://multimedia.3m.com/mws/media/466120O/esr.pdf

@@

Space applications where it is used to study interactions between the natural space radiation environment and space hardware or astronauts;
Medical applications where interactions of radiations used for treatment are simulated.
Radiation effects in microelectronics where ionizing effects on semiconductor devices are modeled.
Nuclear physics

@@

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.3\textwidth,origin=c,angle=0]{images/satellite.png}
 \qquad
 \includegraphics[width=.5\textwidth,origin=c,angle=90]{images/cad_sat.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The scintillator on the left and the box holding the setup on the right}
 \end{figure}

@@

\begin{figure}
\includegraphics[width=150.0mm]{images/calibration_photon_yield.png}[H!]
\caption{The satellite radiated by a pencil beam of 10.000 $\gamma$ particles. The scattered $\gamma$s induce signal in the scintillator}
\end{figure}

@@

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=0.45\textwidth,origin=c,angle=0]{images/alt_600km_AE-8_MIN_averaged_spectra.png}
 \qquad
 \includegraphics[width=.45\textwidth,origin=c]{images/alt_600km_AE-8_MAX_averaged_spectra.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The scintillator on the left and the box holding the setup on the right}
 \end{figure}

@@

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.45\textwidth,origin=c,angle=0]{images/alt_600km_AP-8_MIN_averaged_spectra.png}
 \qquad
 \includegraphics[width=.45\textwidth,origin=c]{images/alt_600km_AP-8_MAX_averaged_spectra.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The scintillator on the left and the box holding the setup on the right}
 \end{figure}

\pagebreak
\section{Conclusion}

@@

>>>>

We are designing a fleet of nanosatellites to perform accurate position determinations
of short-duration gamma-ray bursts by measuring arrival time differences.
To achieve sufficient photon statistics to measure the arrival times
precisely under the severe limitations of size, mass, and power consumption,
we propose the use of a large-area CsI scintillator that has high light output
and the use of a small-sized multipixel photon counter (MPPC) that has low
power consumption. We plan to use one of the latest-model MPPCs provided
by Hamamatsu Photonics, which has an active area of 6  6 mm2. We have compared the performance of two scintillators of different sizes (150 75  5 mm3 and 100  75  5 mm3); the bigger one is the maximum size that can be mounted on a three-unit satellite, according to CubeSat standards.
We have found that the two scintillators have similar light yields and each has an energy threshold of $\sim$10 keV at 25C. We have also examined the position dependence of the light yield by using radiation from 241Am (59.5 keV) source, and have confirmed that uniformity was improved by using two MPPCs for signal readout.

@@

@@

Space applications where it is used to study interactions between the natural space radiation environment and space hardware or astronauts; Medical applications where interactions of radiations used for treatment are simulated. Radiation effects in microelectronics where ionizing effects on semiconductor devices are modeled.

\subsection{The experimental setup}

We are designing a fleet of nanosatellites to perform accurate position determinations
of short-duration gamma-ray bursts by measuring arrival time differences.
To achieve sufficient photon statistics to measure the arrival times
precisely under the severe limitations of size, mass, and power consumption,
we propose the use of a large-area CsI scintillator that has high light output
and the use of a small-sized multipixel photon counter (MPPC) that has low
power consumption. We plan to use one of the latest-model MPPCs provided
by Hamamatsu Photonics, which has an active area of 6  6 mm2. We have compared the performance of two scintillators of different sizes (150  75  5 mm3 and 100  75  5 mm3); the bigger one is the maximum size that can be mounted on a three-unit satellite, according to CubeSat standards.
We have found that the two scintillators have similar light yields and each has an energy threshold of $\sim$10 keV at 25C. We have also examined the position dependence of the light yield by using radiation from 241Am (59.5 keV) source, and have confirmed that uniformity was improved by using two MPPCs for signal readout.

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/spectracsitl.png}
\caption{The reflectivity $\cite{scinti}$ of the ESR tape that was used to wrap the scintillator in order to increase the light yield. This data was included in the simulation.}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/qe.png}
\caption{The reflectivity $\cite{esr}$ of the ESR tape that was used to wrap the scintillator in order to increase the light yield. This data was included in the simulation.}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/reflectivity.png}
\caption{The photon detection efficiency $\cite{qe}$ of the MPPCs used for the readout of the scintillators. This data was included in the simulation.}
\end{figure}

ESR foil

QE \cite{qe} of the MPPC

esr \cite{esr} foil:
Please check "ESR from 3M" company. e.g.,
%http://multimedia.3m.com/mws/media/466120O/esr.pdf

@@

The direction of GRBs is isotropic in the sky as they are extragalactic objects. As the positioning of the scintillators is not decided yet it is important to understand which configuration would be the best for detecting as many GRBs as possible. Therefore it is vital to understand how the material of the satellite itself absorbs $\gamma$s. The satellite consists of several modules with specific shapes and material contents. Therefore building up the whole geometry and material composition was not possible in Geant4, thus the model of the satellite had to be  imported into Geant4.

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.3\textwidth,origin=c,angle=0]{images/satellite.png}
 \qquad
 \includegraphics[width=.5\textwidth,origin=c,angle=90]{images/cad_sat.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The CAD model of the satellite (on the right) and the view of the imported model in Geant (on the left)}
 \end{figure}

Importing predefined CAD models into GEANT4 is not always possible or requires intermediate file format conversion to Geometry Description Markup Language (GDML) using commercial or third party software. CADMesh \cite{cadmesh} is a direct CAD model import interface for GEANT4 leveraging ASSIMP \cite{assimp} for reading the CAD files. In this work the CAD model of the satellite was exported to STL files. These files were imported by the CADMesh software to Geant4. The tesselation was done by the TETGEN \cite{tetgen} software.

@@

\begin{figure}
\includegraphics[width=150.0mm]{images/calibration_photon_yield.png}[H!]
\caption{The spectra of 11 million photons taken experimentally (blue histogram) matched up with the results of the simulation (green histogram) and the Gaussian fitted to the simulated data}
\end{figure}

@@

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=0.45\textwidth,origin=c,angle=0]{images/alt_500km_AE-8_MIN_averaged_spectra.png}
 \qquad
 \includegraphics[width=.45\textwidth,origin=c]{images/alt_500km_AE-8_MAX_averaged_spectra.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:band500e} The spatially avaraged band function (differential flux for a given energy band, solid line) and the integrated band function (dotted line) of electrons at an altitude of 500 km for solar minimum (left) and solar maximum (right) }
 \end{figure}

@@

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.45\textwidth,origin=c,angle=0]{images/alt_500km_AP-8_MIN_averaged_spectra.png}
 \qquad
 \includegraphics[width=.45\textwidth,origin=c]{images/alt_500km_AP-8_MAX_averaged_spectra.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:band500p} The spatially avaraged band function (differential flux for a given energy band, solid line) and the integrated band function (dotted line) of protons at an altitude of 500 km for solar minimum (left) and solar maximum (right) }
 \end{figure}

Put 4 spectra here from the 4 direction to the satellite. Quantify the detected photons by summing up all entries. Where should be the treshold?

\section{Conclusion}

@@

\bibitem{cadmesh} Poole, C. M. and Cornelius, I. and Trapp, J. V. and Langton, C. M., A CAD Interface for GEANT4, Australasian Physical \& Engineering Science in Medicine, 2012

\bibitem{assimp} http://www.assimp.org/

\bibitem{tetgen} Hang Si. 2015. "TetGen, a Delaunay-Based Quality Tetrahedral Mesh Generator". ACM Trans. on Mathematical Software. 41 (2), Article 11 (February 2015), 36 pages

\bibitem{scinti} http://www.amcrys.com/pdf/4279\_.pdf

\bibitem{qe} http://www.hamamatsu.com/resources/pdf/ssd/s13360\_series\_kapd1052e.pdf

\bibitem{esr} http://multimedia.3m.com/mws/media/466120O/esr.pdf
